---
title: "World Happiness"
subtitle: "Interactive Slides Using xaringan"
author: "Presented by: Geshin Aderemi"
date: "Last updated: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts, custom-style.css]
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    #chakra: "remark.js"
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(tidy = FALSE, tidy.opts = list(width.cutoff = 40))
library(tidyverse)
library(rio)
library(lubridate)
library(plotly)
library(ggpmisc)
library(maps)
library(png)
```


# Table of Contents


##World Happiness

- Objective
- Telling the Story with Data
- Conclusion
- Appendix

---


# Objective


Identify if there are .green[demographic], and/or .light_grey[economic] factors that contribute to a .blue[happier] life.


---

.pull-left[
## .blue[Population]

Little to no correlation between happiness and population

]

.pull-right[

 
```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}

  health_pop <- import("happiness_2015_2017.csv") %>% 
  select("Country", 
         happiness = "Happiness Score" )

  population <- import("population_2017.csv") %>% 
  select("Country", 
         population = "Population")

  data <- left_join(population, health_pop, by="Country") %>% 
    na.omit()

  pop_graph <- ggplot(data, aes(x = log(population), y = log(happiness)))+
   geom_point()+
   stat_smooth(method = "lm",
               se = FALSE)+
   labs(x = "Population", y = "Happiness Score")
 
 ggplotly(pop_graph)
```

]


---

.pull-left[
## .blue[Health]

Strong correlation between **happiness and health(life expectancy)**

Are **happy people healthy**, or are **healthy people happy**?

What contributes to a **longer life expectancy**?


]


.pull-right[
```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}

  happiness_data <- import("happiness_2015_2017.csv") %>% 
  select(happiness = "Happiness Score", 
         health = "Health (Life Expectancy)")

 my_graph <- ggplot(happiness_data, aes(x = happiness, y = health))+
   geom_point()+
   stat_smooth(method = "lm",
               se = FALSE, 
               size = 1)
 
 ggplotly(my_graph)
```

]

---

.pull-left[
## .blue[Economy (GDP per Capita)]

Strong correlation between **happiness and GDP**

Are **happy people in high-income countries**, or are **people in high-income countries happy**?


]


.pull-right[
```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}

   happiness_data <- import("happiness_2015_2017.csv") %>% 
  select(health = "Health (Life Expectancy)", 
         gdp = "Economy (GDP per Capita)")

 health_gdp <- ggplot(happiness_data, aes(x = gdp, y = health))+
   geom_point()+
   stat_smooth(method = "lm",
               se = FALSE, 
               size = 1)
 
 ggplotly(health_gdp)
```

]

---

## .blue[Wealth]

- Strong correlation between **Gross Domestic Product (GDP) and health**

- Even stronger correlation between **GDP and Happiness**

- **Richer countries have higher average happiness levels**

.pull-left[
```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", out.height="20%"}

  happiness_data <- import("happiness_2015_2017.csv") %>% 
  select(health = "Health (Life Expectancy)", 
         gdp = "Economy (GDP per Capita)")

 health_gdp <- ggplot(happiness_data, aes(x = gdp, y = health))+
   geom_point()+
   stat_smooth(method = "lm",
               se = FALSE, 
               size = 1)
 
 ggplotly(health_gdp)
```

]

.pull-right[
```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="100%", out.height="10%"}

  happiness_data <- import("happiness_2015_2017.csv") %>% 
  select(happiness = "Happiness Score", 
         gdp = "Economy (GDP per Capita)")

  happiness_gdp<- ggplot(happiness_data, aes(x = happiness, y = gdp))+
   geom_point()+
   stat_smooth(method = "lm",
               se = FALSE, 
               size = 1)
 
 ggplotly(happiness_gdp)
```

]

---
class: center
# Conclusion



.column[ .green[Wealthier] countries and ones that have sustained economic growth tend to have higher             average .blue[happiness] levels.

]

.column[.orange[Healthier] countries also tend to have a .blue[happier] population. 

However, .orange[healthier] countries also tend to be .green[wealthy].
]
    
.column[   *Evidence suggests that .blue[wealth], .orange[health], and .blue[happiness] go together.



*Does not mean there is causal effect. Further analysis needed
]

---

# References

 - Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan)
 
 - The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](https://yihui.org/knitr), and [R Markdown](https://rmarkdown.rstudio.com).
 
 - World Happiness Report dataset from [kaggle.com](https://www.kaggle.com/datasets/unsdsn/world-happiness)

 - Inspiration for the the visualization from [Kevin Hart](https://www.youtube.com/watch?v=Akt3SdKL4yM)










